When are Fuzzy Extractors Possible?

### 2014-10-01 trunk/info-bounds/FuzzyExtPossibility.tex
added a bunch of restructuring suggestions for the intro

\section{Introduction}
\anote{should our results be seen as justifying the distribution specific approach?}
\anote{make the point that narrowing the family $\mathcal{W}$ makes the security guarantees much more brittle}
Usually, authentication requires some high quality secret.  Traditionally, this secret is assumed to have high min-entropy.  However, many sources with sufficient entropy for authentication present an additional problem: noise~\cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password,pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical,bennett1988privacy}.  That is, when the physical instantiation of the source is read multiple times, readings are close~(according to some metric) but not identical.  To use such sources in an authentication scheme it is often necessary to remove this noise and derive the same key from the initial and subsequent readings.

This problem was introduced in the seminal work of Bennett, Brassard, and Roberts~\cite{bennett1988privacy}.  They identify two fundamental tasks in noisy key derivation.  The first is known as information-reconciliation, removing the noise without leaking significant information, and the second is privacy amplification, converting the high entropy secret to a uniform random value.  In this work, we consider the non-interactive version of these problems where these tasks are performed with a single message.

@@

@@

Consider a user, Alice, using a noisy secret to authenticate with a remote server, Bob.  In this setting, Alcie could initially send the value $w$ to Bob and then authenticate with subsequent value $w'$.  If the server holds $w$ and the user $w'$ the two parties can agree on a key using an interactive protocol.\footnote{It is dangerous to allow a remote server access to original reading $w$ as they can then impersonate the user.  Ideally, the server would keep a ``hashed'' value of $w$.  This is  done for noiseless secrets like passwords.}  In this world, secure two-party computation can produce a key whenever the distribution $W$ has fuzzy min-entropy.
In the one-message setting, we are far from this ideal.

@@

\paragraph{The price of distributional uncertainty}
Fuzzy extractors are designed with limited knowledge of the distributions that will later be used.  Traditionally, the distribution $W$ is assumed to be an arbitrary distribution with min-entropy.  Making minimal assumptions about the distribution $W$ is desirable for two reasons: 1) for high entropy distributions, only a small part of the distribution has been observed 2) the adversary may have some side information about the distribution $W$ and thus the adversaries view of the distribution is different than that of the algorithm designer.  Fuzzy extractors support a family of distributions $\mathcal{W}$ and hope that the target distribution $W\in\mathcal{W}$.

@@

\paragraph{Positive Results} %We first consider the \emph{distribution-aware} setting.  
We show a distribution-aware secure sketch for every source with super-logarithmic fuzzy min-entropy with super-logarithmic output entropy~(\thref{cons:leveling}).  Using the sketch-and-extract construction, there is a distribution-aware fuzzy extractor with super-logarithmic key output length.\footnote{Assuming exponential-hard pseudorandom generators, a super-logarithmic length key can be expanded to an arbitrary length.  In this work, we assume the goal is to produce a super-logarithmic length key.  In the information-theoretic setting, this can be seen as a minimum requirement for security.}  Thus, in the distribution-aware setting, fuzzy min-entropy is both a necessary and sufficient condition for security.

@@

\paragraph{Computational security?}
Our negative result on information-theoretic secure sketches extends to secure sketches where $w$ has pseudoentropy~\cite{DBLP:journals/siamcomp/HastadILL99} using a result of Fuller et al.~\cite{fuller2013computational}.  Secure sketches that provide computational unpredictability of $w$ are constructible from semantically secure multi-linear encodings~\cite{BitanskyCKP14}.  Semantically secure multi-linear encodings are a very strong assumption and unpredictability is weaker than pseudoentropy.  Converting unpredictability to a key requires a special type of extractor known as a reconstructive randomness extractor~\cite{barak-computational, DBLP:conf/eurocrypt/HsiaoLR07}.

>>>>

\section{Introduction}
\anote{should our results be seen as justifying the distribution specific approach?}
\anote{make the point that narrowing the family $\mathcal{W}$ makes the security guarantees much more brittle}
Usually, authentication requires some high quality secret.  Traditionally, this secret is assumed to have high min-entropy.  However, many sources with sufficient entropy for authentication present an additional problem: noise~\cite{daugman2004,zviran1993comparison,brostoff2000passfaces,ellison2000protecting,mayrhofer2009shake,monrose2002password,pappu2002physical,tuyls2006puf,gassend2002silicon,suh2007physical,bennett1988privacy}.  That is, when the physical instantiation of the source is read multiple times, readings are close~(according to some metric) but not identical.  To use such sources in an authentication scheme it is often necessary to remove this noise and derive the same key from the initial and subsequent readings. \lnote{Why limit to authentication}

 This problem was introduced in the seminal work of Bennett, Brassard, and Roberts~\cite{bennett1988privacy} \lnote{BBR application was not, in fact, authentication}. \lnote{I just realized (after a talk at Allerton) that we are neglecting Wyner's 1975 wiretap channel and follow-up work, which also studied this problem}  They identify two fundamental tasks in noisy key derivation.  The first is known as information-reconciliation, removing the noise without leaking significant information, and the second is privacy amplification, converting the high entropy secret to a uniform random value.  In this work, we consider the non-interactive version of these problems where these tasks are performed with a single message.

@@

\lnote{I am thinking the sketch paragraph should go later, after necessary condition, b/c the necessary condition is for F.E.}

@@

\lnote{The below needs a title and clearer form: ``When is the necessary condition sufficient?'' Two answers, both computational: general MPC under relatively benign assumptions but interaction or obfuscation with crazy assumptions but no interaction}

Consider a user, Alice, using a noisy secret to authenticate with a remote server, Bob.  In this setting, Alcie could initially send the value $w$ to Bob and then authenticate with subsequent value $w'$.  If the server holds $w$ and the user $w'$ the two parties can agree on a key using an interactive protocol.\footnote{It is dangerous to allow a remote server access to original reading $w$ as they can then impersonate the user.  Ideally, the server would keep a ``hashed'' value of $w$.  This is  done for noiseless secrets like passwords.}  In this world, secure two-party computation can produce a key whenever the distribution $W$ has fuzzy min-entropy.
In the one-message setting, we are far from this ideal. \lnote{Why frame it this way, effectively introducing a new scenario, when we could appeal to the first paragraphs of the intro and simply say ``consider, for a moment, removing the requirement that these tasks are performed with a single message''? Also a paper to cite: ``Secure computation w/o authentication'' by some superset of Canetti and Rabin; the reason we should cite this one rather than general MPC is that we don't want to assume authenticated channels here to start with}

\lnote{I don't think you want to talk about traditional constructions here yet. I think what you want to say, in light of the previous computational paragraph, is ``what about information-theoretic: is the necessary condition also sufficient''?}

@@

\paragraph{The price of distributional uncertainty}

\lnote{I think this should be ``Our Contributions'' and go in the following order. Our main contribution is to show that, if your FE works for a sufficiently rich class of distributions, this condition is not sufficient. On the other hand, in the extreme case of custom-building for a totally known distribution, we show (non-poly-time) construction that works. We also consider the same question for what has traditionally been the main building block of FE, ``secure sketch'' (appeal to the already-defined-above notion of information reconciliation and introduce the briefly). We show an even tighter impossibility result for FE, as well as (non-poly-time) possibility result}

The question of whether the necessary condition is also sufficient depends on the class of distributions for which your construction needs to work. First, negative result (which is most important)

Fuzzy extractors are designed with limited knowledge of the distributions that will later be used.  Traditionally, the distribution $W$ is assumed to be an arbitrary distribution with min-entropy.  Making minimal assumptions about the distribution $W$ is desirable for two reasons: 1) for high entropy distributions, only a small part of the distribution has been observed 2) the adversary may have some side information about the distribution $W$ and thus the adversaries view of the distribution is different than that of the algorithm designer.  Fuzzy extractors support a family of distributions $\mathcal{W}$ and hope that the target distribution $W\in\mathcal{W}$.

@@

\paragraph{Positive Results} %We first consider the \emph{distribution-aware} setting.  \lnote{I think this framing gives positive results too much attention. As we discussed on Monday, positive results here aren't what we want to emphasize}
We show a distribution-aware secure sketch for every source with super-logarithmic fuzzy min-entropy with super-logarithmic output entropy~(\thref{cons:leveling}).  Using the sketch-and-extract construction, there is a distribution-aware fuzzy extractor with super-logarithmic key output length.\footnote{Assuming exponential-hard pseudorandom generators, a super-logarithmic length key can be expanded to an arbitrary length.  In this work, we assume the goal is to produce a super-logarithmic length key.  In the information-theoretic setting, this can be seen as a minimum requirement for security.}  Thus, in the distribution-aware setting, fuzzy min-entropy is both a necessary and sufficient condition for security.

@@

\paragraph{Computational security?} \lnote{I think this ought to move to the ``Is the necessary condition sufficient'' before ``our results''}
Our negative result on information-theoretic secure sketches extends to secure sketches where $w$ has pseudoentropy~\cite{DBLP:journals/siamcomp/HastadILL99} using a result of Fuller et al.~\cite{fuller2013computational}.  Secure sketches that provide computational unpredictability of $w$ are constructible from semantically secure multi-linear encodings~\cite{BitanskyCKP14}.  Semantically secure multi-linear encodings are a very strong assumption and unpredictability is weaker than pseudoentropy.  Converting unpredictability to a key requires a special type of extractor known as a reconstructive randomness extractor~\cite{barak-computational, DBLP:conf/eurocrypt/HsiaoLR07}.
